\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 and academicon fonts
%% and packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}


% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Lato}
\else
  % If using pdflatex:
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{Black}{HTML}{000000}
% \colorlet{name}{black}
\colorlet{tagline}{VividPurple}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
% \colorlet{subheading}{PastelRed}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{Black}
\colorlet{body}{SlateGrey}

% Change some fonts, if necessary
% \renewcommand{\namefont}{\Huge\rmfamily\bfseries}
% \renewcommand{\personalinfofont}{\footnotesize}
% \renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
% \renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Aman Nijjar}
\tagline{Fourth Year Computer Engineering Undergraduate}
\personalinfo{
  % You can add your own with \printinfo{symbol}{detail}
  \email{anijjar@uvic.ca}
  \phone{604-500-5071}
  \mailaddress{11988 237st, Maple Ridge, BC V4R 2C8}
 % \location{Sunnyvale, CA}
  %\homepage{marissamayr.tumblr.com}
  %\twitter{@marissamayer}
  \linkedin{ca.linkedin.com/in/anijjar19}
  \github{github.com/anijjar}
}

\makecvheader

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}

\cvsection{Summary of Qualifications}
\begin{itemize}
\item President of AUVIC: Leading a 15-member team to build an autonomous underwater vehicle (AUV) called Trident.
\item Integrated SocketCAN drivers for ROS from ros\_canopen and built a C++ message handler to link the AUV embedded system to the ROS framework during the workterm with AUVIC.
%\item Practiced cross-platform development for ROS systems.
\item Created sprints and assigned issues to members of AUVIC using Jira.
\end{itemize}

\cvsection{Relevant Competencies}

%\divider

% \cvsubsection{Electrical Diagnostics}
% \begin{itemize}
%     \item 
%     \item Created Schematic capture of a pinging circuit. 
%     \item 
% \end{itemize}

%\divider

\cvsubsection{Robotics}
\begin{itemize}
    \item  Compiled a list of mechanical constraints for an AUV such as keeping all high power hardware in the same CNC enclosure, adding bouyancy devices to ensure positive bouyancy, material selection, etc.
    \item  Used multiple programming languages (C/C++/Python) to link ROS noetic on Ubuntu Focal with the AUV embedded system at AUVIC to send messages over a CAN bus. 
    \item  Programmed C I2C firmware on a FreeRTOS device to program a temperature sensor and a humidity sensor.
\end{itemize}

\divider

\cvsubsection{Electrical Design}
\begin{itemize}
    \item Built Symbols and Footprints for integrated circuits on Altium Designer.
    \item Created Schematic capture of a pinging circuit on Altium Designer. 
    \item Created a layout of a pinging circuit on Altium Designer.
\end{itemize}

%\cvsubsection{Electrical Drive Systems}
%\begin{itemize}
%    \item Comfortable with load torque analysis of DC, induction, and Syncronous motors.
%    \item Comfortable with speed control analysis of DC, Induction, and Syncronous motors.
%    \item Comfortable with braking analysis of DC, Induction, and Syncronous motors.
%\end{itemize}

\divider

\cvsubsection{Quality Assurance/Control}
\begin{itemize}
    \item Unit Testing: Used gunit and unittest to confirm if my C++ methods are giving the expected output.
    \item Integration Testing: Introduced Travis CI to AUVIC to run build tests on ros nodes, C++ methods, and Python scripts before merging pull requests.
    \item Created an electrical overview to show the power requirements and communication buses of AUVIC's embedded system to members.
\end{itemize}

\cvsection{Projects}
\cvsubsection{Haze Removal - C++ Image Processing}
This command line application removes fog and haze in images by using dark channel prior and several other filters. This is based on a Matlab script from Rachel Yuen at UW-Madison. ROS lacks Matlab support, so I rewrote the script in C++ to test it on AUVIC's AUV.

\divider

%\cvsubsection{Audio-Effects PCB - C Signal Proccessing}
%An embedded application for the STM32F0xx discovery board.This board takes an audio signal and then filters it with a butterworth filter before entering the ADC on the STM. The STM then applies either an echo or pitching effect to the signal via buttons  before being sent out of the DAC to be played through a headphone speaker for everyone to enjoy.

%\divider

%\cvsubsection{Street Traffic Simulator - C Real-Time Operating Systems}
%Simulates a one way street with a traffic light at different rates of traffic via LEDs. Uses 4 RTOS tasks and communicates with one another using queues. Rate of traffic is adjusted using a potentiometer.

%\divider

\cvsubsection{Aircraft Weight Shifter -  Electrical Drive Systems}
Presented a weight shifting solution for an aircraft using requirements my professor was given. Its purpose was to adjust an aircrafts centre of gravity to reduce its pitching moment.

%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

\cvsection{Work/Volunteer\\ Experience}
\cvevent{Junior Electronics Engineer Intern}{Autonomous Underwater Vehicle Interdisciplinary Club (AUVIC)}{May 2020 -- Ongoing}{Victoria, BC}
\begin{itemize}
\item Used Altium Designer and LTspice to design a pinging circuit to operate underwater for validating an AUV Hydrophone system.
\item Introduced continuous integration with Travis CI and agile workflows with Jira.
\item Developed a ROS package using ros\_canopen that sends frames to the CAN bus.
\end{itemize}

\divider\smallskip

\cvevent{Ship2Shore/Science-Symposium}{Ocean Networks Canada (ONC)}{May 2019}{Victoria, BC}
Ran an activity for middle school students who are interested in engineering.

% keep 4 max
\cvsection{Skills}
\cvskill{C/C++/Python}{4}
%\cvskill{Python}{4}
%\cvskill{Cross-platform dev.}{3}
\cvskill{Altium Designer}{3}
\cvskill{FreeRTOS}{4}
%\cvskill{Soldering}{5}
%\cvskill{Oscilloscope}{3}
%\cvskill{Logic Analyzer}{3}
%\cvskill{Signal Generator}{3}

\cvsection{Education}
\cvevent{Bachelor of Computer Engineering}{University of Victoria}{Sept. 2016 - Ongoing}{Victoria, BC}
Relevant courses: CSC 111/115 (C/C++ programming with Engineering applications), ECE 458 (Communication Networks), ECE 255 (Computer Architecture), ECE 241 (Digital Design)

\cvsection{My qualities}
\cvachievement{\faBasketballBall}{Persistence}{I went from a substitute basketball player in my highschool freshman year to a starter by sophmore year.}

\divider

\cvachievement{\faLanguage}{Bilingual}{Fluent in English and Punjabi.}

\end{paracol}

\end{document}
